Engineering momentum profiles of cold-atom beams

### 2019-07-23 Paper/pra_resub/paper.tex
figure 5 revision

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \centerline{\includegraphics[scale=0.45]{figure1appendix_new.pdf}}
\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas for $z_0=a$ (red curve), $z_0=-a$ (blue curve) 
($a>0$, the exact value of $a$ is not important for our discussion). 
 Note that the minimum of the density is at $-a$. 
The shaded area is a combination of the two solutions with the singularity at $z=0$. 
Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
 \label{fig:Fig1}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \begin{figure}
 \centerline{\includegraphics[scale=0.45]{figure5_corrected.pdf}}
\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas  
for $z_0=a$ (solid red curve), $z_0=-a$ (dot-dashed blue curve)
($a>0$, the exact value of $a$ is not important for our discussion).
  Note that the minimum of the density is at $-a$.
The shaded area is a combination of the two solutions with the  
singularity at $z=0$.
Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities  
from {\bf a)}.}
 \label{fig:Fig1}
 \end{figure}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
